---
title: "Complex Analysis Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Complex Analysis Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette runs protein complex analysis from R without a Shiny session. The
workflow starts from QC statistics, selects a complex database, filters to one
organism, scores matching complexes, and returns a display-ready result table.

```{r load-input}
library(complexbrowser)

input_file <- complexbrowser_extdata_path("examples", "myo.csv")
input <- read.csv(input_file, check.names = FALSE)

qc <- complexbrowser_run_qc(
  data = input,
  no_cond = 6,
  no_rep = 3,
  log2 = FALSE,
  grouped = TRUE,
  q_values = TRUE,
  normalization = NULL,
  design = "unpaired"
)
```

Run complex analysis with the bundled CORUM database. The `organism` value must
match the organism labels used in the selected database.

```{r run-complex-analysis}
complex <- complexbrowser_run_complex_analysis(
  stats = qc$stats,
  database = "CORUM",
  organism = "Human",
  no_cond = 6,
  no_rep = 3,
  database_name = "CORUM"
)

complex$metadata
```

The result includes the filtered statistics, filtered database rows, score
matrix, scored database, display table, and metadata. The display table is the
same table shape used by the Shiny app download.

```{r inspect-complexes}
display_columns <- c(
  "ComplexID",
  "Complex_Name",
  "NUS",
  "NQS",
  "Coverage",
  "FC C2/C1",
  "Noise"
)

head(complex$display_table[, display_columns])
```

ComplexBrowser can also generate a short condition-specific summary from the
scored database. Lower `noise_threshold` values make this summary more
selective.

```{r summarize-complexes}
summary_text <- complexbrowser_complex_summary(
  complex$scored_database,
  no_cond = 6,
  no_rep = 3,
  condition = 2,
  noise_threshold = 0.5
)

cat(summary_text)
```

Write the complex table when using the result in a command-line or pipeline
workflow.

```{r write-output, eval=FALSE}
complexbrowser_write_complex_table(
  complex$display_table,
  file = "myo-corum-complexes.csv"
)
```
