---
title: "Quality Control Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quality Control Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette runs the ComplexBrowser quality-control workflow from R without a
Shiny session. The example data are bundled with the package and contain raw
protein intensities for six conditions with three replicates per condition.
q-value columns are already present in the input file.

```{r load-input}
library(complexbrowser)

input_file <- complexbrowser::complexbrowser_extdata_path("examples", "myo.csv")
input <- read.csv(input_file, check.names = FALSE)

dim(input)
names(input)[1:8]
```

Run QC with the same settings that would be selected interactively in the Shiny
app. `log2 = FALSE` tells ComplexBrowser that the intensity values are still on
the raw scale. `grouped = TRUE` means replicate columns are adjacent by
condition. `q_values = TRUE` means statistical columns are read from the input
instead of being calculated with LIMMA.

```{r run-qc}
qc <- complexbrowser_run_qc(
  data = input,
  no_cond = 6,
  no_rep = 3,
  log2 = FALSE,
  grouped = TRUE,
  q_values = TRUE,
  normalization = NULL,
  design = "unpaired"
)

qc$metadata
dim(qc$merged_table)
```

The returned object contains the prepared input, the statistics object used by
later workflows, a merged display table, and metadata.

```{r inspect-qc}
qc_columns <- c(
  "ProteinID",
  "Mean intensity C1",
  "Mean intensity C2",
  "Condition_1_CV",
  "Condition_2_CV",
  "qValue C2"
)

head(qc$merged_table[, qc_columns])
```

The QC report helper prepares the compact summary tables used by the Shiny
report template. These tables are often enough for scripted checks or quick
inspection.

```{r report-data}
report_data <- complexbrowser_prepare_qc_report_data(
  qc$stats,
  no_cond = 6,
  no_rep = 3
)

report_data$VAL_t
report_data$CV_t
```

Write the merged statistics table when another tool needs to consume the QC
result.

```{r write-output, eval=FALSE}
complexbrowser_write_input_statistics(
  qc$merged_table,
  file = "myo-qc-statistics.csv"
)
```
